%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{4mm}
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Software Engineer} % Job title
    {Moreh Corp.} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a dedicated prefill engine that parallelizes long-context LLM prefill across multi-node GPU clusters using context parallelism (Ulysses + Ring Attention with zigzag load balancing), achieving sub-1s TTFT for 32K/64K contexts for gpt-oss-120b model and enabling utilization of legacy GPUs in heterogeneous clusters. Implemented FlashAttention-style Triton kernels for context window attention with attention sinks.}
        \item {Implemented a full-stack distributed machine learning framework, from user-level Python libraries (e.g., PyTorch) to GPU kernels, including the intermediate representation of computational graphs, a graph-level cost model for execution time prediction, and the compiler that leverages it to produce optimal execution plans.}
        \item {Profiled and optimized performance bottlenecks across models and data transfer routines.}
        \item {Diagnosed and rectified training anomalies, improving overall model reliability and performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{4mm}
  \cventry
    {Software Engineer} % Job title
    {\mycompany{}. Co., Ltd.} % Organization
    {Gyeonggi-do, S.Korea} % Location
    {Feb. 2019 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Windows API compatibility layers in Linux to run Windows binaries on \mycompany{}, a Linux-based operating system.}
	\item {Designed and developed proxy functions for Windows inter-process COM calls, bridging Windows/Linux calling conventions using runtime x86 machine code generation and inline assembly.}
	%\item {Developed an RPC server for \mycompany{} from scratch, mimicking the Windows counterpart}  
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
\vspace{4mm}