%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
  My research interests are persistent memory and storage systems.\\
\begin{cventries}


  \cventry
    {June-hyung Kim, \textbf{Jangwoong Kim}, Hyeongu Kang, hang-Gyu Lee, Sungyong Park, Youngjae Kim} % Affiliation/role
    {pNOVA: Optimizing Shared File I/O Operations of NVM File System on Manycore Servers} % Organization/group
    {Hangzhou, China.} % Location
    {2019} % Date(s)
    {
      10th ACM SIGOPS Asia-Pacific Workshop on Systems (APSys), 2019.
    }

  \cventry
	{\textbf{Jangwoong Kim}, June-Hyung Kim, Youngjae Kim,  Sungyong Park.}
	{Parallelizing a Single File Write Operation of Non-Volatile Memory File Systems.}
	{Pyeongchang, S.Korea.}
	{2018}
	{
		Korea Software Congress (KSC), 2018. \textcolor{red}{[Best Paper of Computer System]}
	}

  \cventry
	{\textbf{Jangwoong Kim},  Awais Khan,  Youngjae Kim,  Sungyong Park.}
	{Understanding the performance of storage class memory file systems in the NUMA architecture.}
	{Journal}
	{2018}
	{
		The Journal of Networks, Software Tools and Applications (Cluster Computing), 2018.
	}

  \cventry
	{\textbf{Jangwoong Kim}, Jae-Hoon Kim,  Awais Khan,  Youngjae Kim,  Sungyong Park.}
	{ZonFS: A Storage Class Memory File System with Memory Zone Partitioning on Linux.}
	{Arizona, US.}
	{2017}
	{
		The 5th International Workshop on Autonomic Management of Grid and Cloud Computing (AMGCC), 2017.
	}


\end{cventries}

\clearpage
